Visualize ukb whole genome, using ctwas results

### 2023-04-20 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_03212023.Rmd
more simulation settings for low SNP PVE

---
title: "Simulations to test ctwas summary stats version, 45k samples"
output: html_document
---

@@

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210416/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20210416_compare/"
runtag = "ukb-s80.45-adi"
configtags = 1
simutags = paste(rep(1:2, each = length(1:5)), 1:5, sep = "-")

@@

## Data

  * **GWAS summary statistics** we simulated summary statistics data with different causal gene/SNP proportion and PVE. To simulate this data, we need the following:
      * **genotype data** we used is from UKB biobank, randomly selecting `r as.character(n.ori)` samples. We then filtered samples.
      The columns selected for filtering samples are as follows:
        * sex (31)
        * UK Biobank assessment centre (54)
        * age (21022)
        * genetic ethnic grouping (22006)
        * genetic sex (22001)
        * genotype measurement batch (22000)
        * missingness (22005)
        * genetic PCs (22009-0.1 - 22009-0.40)
        * genetic relatedness pairing (22011)
        * genetic kinship (22021)
        * outliers (22027)

        We filtered the samples based on the following criteria:  
        1. Remove all rows in which one or more of the values are missing, aside from the in the "outlier" and "relatedness_genetic" columns. This step removes any samples that are not marked as being "White British".  
        2. Remove rows with mismatches between self-reported and genetic sex  
        3. Remove "missingness" and "heterozygosity" outliers as defined by UK Biobank. 
        4. Remove any individuals have at least one relative  
        5. Remove any individuals that have close relatives identified from the "relatendess" calculations that weren't already identified using the kinship calculations.

        This ended up with **n = `r as.character(n)` samples**.  We use SNP genotype data from chr 1 to chr 22 combined from UKB. We select SNPs with minor allele frequency > 0.05 and SNPs with at least 95% genotyping rate (5% missing). There are **total = `r as.character(p)` SNPs** passed these filters and go into our analysis.  
    * **Expression models** The one we used in this analysis is GTEx Adipose tissue v7 dataset. This dataset contains ~ 380 samples, **`r as.character(J)` genes** with expression model. [FUSION/TWAS](http://gusevlab.org/projects/fusion/) were used to train expression model and we used their lasso results. SNPs included in eQTL anlaysis are restricted to cis-locus 500kb on either side of the gene boundary. eQTLs are defined as SNPs with abs(effectize) > 1e-8 in lasso results.

      To simulate phenotype data, first we impute gene expression based on expression models, then we set gene/SNP pi1 and PVE, get rough effect size for causal SNPs and genes and simulate phenotype under the sparse model with spike and slab prior.
      Then we performed GWAS for all SNPs and get z scores for each by univariate linear regression.

  * **LD genotype reference**
  We used the genotype of 2k samples from UKbiobank (randomly selected from the samples used in simulations) to serve as the LD reference.

  * **Expression models**  
  We used GTEx Adipose tissue v7 dataset, the same as used for simulating phenotypes.

@@

`L = 3` , after parameter estimation, for running susie for all regions.

`group_prior = NULL`, the intiating prior parameters we used for running susie for each region is uniform prior for genes and SNPs.

`group_prior_var = NULL`, the intiating prior variance parameters we used for running susie for each region follows susie_rss's default (50).

@@

# Power estimation

```{r power}
simutag <- "1-1"
niter <- 1000
snp.p <- 5e-8
gene.p <- 1e-5
source(paste0(outputdir, "simu", simutag, "_param.R"))
load(paste0(outputdir, runtag, "_simu", simutag, "-pheno.Rd"))
```

We select run `r simutag`  as an example.

* For SNPs. $\pi_1 =$ `r pi_theta` , effect size = `r phenores[["batch"]][[1]][["sigma_theta"]]`, PVE = `r phenores$param$pve.snp.truth`. Power at `r as.character(snp.p)` p value cutoff:

```{r snp}
load("data/power_s80.45.Rd")
# p1 <- pow(niter, n, phenores[["batch"]][[1]][["sigma_theta"]], snp.p)
print(p1)
```

* For genes. $\pi_1 = `r pi_beta`$ , effect size = `r phenores[["batch"]][[1]][["sigma_beta"]]`, PVE = `r phenores$param$pve.gene.truth`. Power at `r as.character(gene.p)` p value cutoff:

```{r gene}
# p2 <- pow(niter, n, phenores[["batch"]][[1]][["sigma_beta"]], gene.p)
print(p2)
# save(p1,p2, file = "data/power_s80.45.Rd")
```

# GWAS/TWAS p value distribution

```{r pvalue}
simutag <- "1-1"
chrom <- 1
source(paste0(outputdir, "simu", simutag, "_param.R"))
load(paste0(outputdir, runtag, "_simu", simutag, "-pheno.Rd"))
```
We select run `r simutag`  as an example.

* For genes. $\pi_1 = `r pi_beta`$ , effect size = `r phenores[["batch"]][[1]][["sigma_beta"]]`, PVE = `r phenores$param$pve.gene.truth`.
TWAS p values and qqplot:

```{r gene-p, message=F, fig.width= 7, fig.height=7}
exprgwasf <- paste0(outputdir, runtag, "_simu", simutag, ".exprgwas.txt.gz")

exprvarf <- paste0(outputdir, runtag, "_chr", chrom, ".exprvar")
exprid <- read_exprvar(exprvarf)[, "id"]
cau <- as.matrix(exprid[phenores[["batch"]][[chrom]][["idx.cgene"]]])
pdist_plot(exprgwasf, chrom, cau)
```
```{r gene-qq, fig.width= 5, fig.height=5}
exprgwas <- fread(exprgwasf, header =T)
gg_qqplot(exprgwas$PVALUE)
```

* For SNPs. $\pi_1 =$ `r pi_theta` , effect size = `r phenores[["batch"]][[1]][["sigma_theta"]]`, PVE = `r phenores$param$pve.snp.truth`.
GWAS p values and qqplot:

```{r snp-p, fig.width= 7, fig.height=7}
snpgwasf <-  paste0(outputdir, runtag, "_simu", simutag, ".snpgwas.txt.gz")

pvarf <- pvarfs[chrom]
snpid <- read_pvar(pvarf)[, "id"]
cau <- as.matrix(snpid[phenores[["batch"]][[chrom]][["idx.cSNP"]]])
pdist_plot(snpgwasf, chrom, cau, thin = 0.1)
```

```{r snp-qq, fig.width= 5, fig.height=5}
snpgwas <- fread(snpgwasf, header =T)
gg_qqplot(snpgwas$PVALUE, thin = 0.1)
```

@@

We have tried to run MR-JTI. The results have higher false postive rate than TWAS. MR-JTI requires the SNPs be pruned before the analysis. It also requires that a gene has at least 20 eQTLs. This resulted in very few genes going into the analysis. Most genes left are in polymorphism dense regions, such as the MHC regions. I ran MR-JTI for top genes in TWAS, around 30-40% of them should be real. However, only a few genes pass MR-JTI’s 20 eQTL requirements and only 1 or 2 (5%) genes are real. We are showing MR-JTI results on this page.

@@

simutags <- paste(1, c(1,2,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(5, c(1, 3:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:4, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(10, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```

# ctwas results (LDR) 
Using the R LD matrices as the LD reference input for ctwas, instead of the genotype type of randomly subsetted samples. The LD R matrices are generated using all 300k samples that passed the our filtering criteria (generated by Wes Crouse). A R matrice is provided for each LD block region.

```{r param3, fig.height=3, fig.width=8, message=F}
configtag <- "1_LDR"
simutags <- paste(1, c(1,2,5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
```

>>>>

---
title: "Simulations to test ctwas summary stats version, 45k samples, a few new setings required"
output: html_document
---

@@

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230321/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230321_compare/"
runtag = "ukb-s80.45-adi"
configtags = 1
simutags = paste(rep(1:9, each = length(1:5)), 1:5, sep = "-")

@@

## Data
The same as 20210416. We tried a few additional settings with small SNP heritablity (0.2) or large gene heritablity (0.5) following the suggestions by reviewers.

@@

`L = 5` , after parameter estimation, for running susie for all regions.

`group_prior = NULL`, the initiating prior parameters we used for running susie for each region is uniform prior for genes and SNPs.

`group_prior_var = NULL`, the initiating prior variance parameters we used for running susie for each region follows susie_rss's default (50).

@@

@@

FOCUS results contains nothing.

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
# plot_focus(configtag, runtag, simutags)
print("FOCUS result is null")
plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(5, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```

### 2023-04-20 analysis/simulation-ctwas-ukbWG-gtex.adipose_s80.45_03222023.Rmd
more simulation settings for low SNP PVE

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230321/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230321_compare/"
runtag = "ukb-s80.45-adi"
configtags = 1
simutags = paste(rep(1:9, each = length(1:5)), 1:5, sep = "-")

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
# plot_focus(configtag, runtag, simutags)
print("FOCUS result is null")
plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(5, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
plot_fusion_coloc(configtag, runtag, simutags)
#plot_focus(configtag, runtag, simutags)
plot_smr(configtag, runtag, simutags)
```

>>>>

```{r files}
pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45_pgenfs.txt"
ld_pgenfn = "/home/simingz/causalTWAS/ukbiobank/ukb_pgen_s80.45/ukb-s80.45.2_pgenfs.txt"
outputdir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230322/" # /
comparedir = "/home/simingz/causalTWAS/simulations/simulation_ctwas_rss_20230322_compare/"
runtag = "ukb-s80.45-adi"
configtags = 1
simutags = paste(rep(1:9, each = length(1:5)), 1:5, sep = "-")

@@

simutags <- paste(1, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# # plot_focus(configtag, runtag, simutags)
# print("FOCUS result is null")
# plot_smr(configtag, runtag, simutags)

simutags <- paste(2, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(3, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(4, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(5, c(1:5), sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(6, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(7, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(8, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)

simutags <- paste(9, 1:5, sep = "-")
plot_par(configtag, runtag, simutags)
plot_PIP(configtag, runtag, simutags)
# plot_fusion_coloc(configtag, runtag, simutags)
# #plot_focus(configtag, runtag, simutags)
# plot_smr(configtag, runtag, simutags)
```

### 2023-04-20 analysis/simulation-ctwas-ukbWG-gtex.adipose_visual.Rmd
more simulation settings for low SNP PVE

plot_all <- function(susief, pf, phenof, colocf = NULL, chr, ldres = NULL, thin = 1){
  a <- fread(susief, header =T)
  setnames(a, old = "id", new = "name")
  b1 <- fread(paste0(pf, ".snpgwas.txt.gz"), header =T)
  b2 <- fread(paste0(pf, ".exprgwas.txt.gz"), header =T)
  setnames(b1, old = "pos", new = "p0")
  b <- rbind(b1, b2, fill = T)
  setnames(b, old = c('PVALUE', 'id'),
         new = c('pvalue', 'name'))

@@

## Zoom view
FP example, LD with causal gene, GNPDA2
under 4-1 to 4-5
```{r sim 2, out.width = "98%", out.height="95%"}
chrom <- 4
runtag <- 4
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

FP example: LD with causal SNP, GALNT10
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- 5
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

under 10-1 to 10-5
FP example: LD with causal SNP
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- 5
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

True positive example: c1orf109
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- 4
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

# region plot with coloc results
```{r sim 2, out.width = "98%", out.height="95%"}
runtag <- "ukb-s80.45-adi"
i <- 4
chrom <- 5
comparedir <- "/project2/mstephens/causalTWAS/simulations/simulation_ctwas_rss_20210416_compare/"
colocfs <- paste0(comparedir, runtag, "_simu", simutags,".Adipose_Subcutaneous.coloc.result")
plot_all(susiefs[i], pfs[i], phenofs[i], chrom, colocf = colocfs[i], thin = 0.01)
```

>>>>

plot_all <- function(susief, pf, phenof, chr, colocf = NULL,  ldres = NULL, thin = 1){
  a <- fread(susief, header =T)
  setnames(a, old = "id", new = "name")
  b1 <- fread(paste0(pf, ".snpgwas.txt.gz"), header =T)
  b2 <- fread(paste0(pf, ".exprgwas.txt.gz"), header =T)
  setnames(b1, old = "pos", new = "p0")
  b <- rbind(b1, b2, fill = T)
  setnames(b, old = c('PVALUE', 'id'),
         new = c('pvalue', 'name'))

@@

## Zoom view
FP example, LD with causal gene, GNPDA2
under 4-1 to 4-5
```{r sim GN, out.width = "98%", out.height="95%"}
chrom <- 4
runtag <- 4
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

FP example: LD with causal SNP, GALNT10
```{r sim GA, out.width = "98%", out.height="95%"}
runtag <- 5
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

under 10-1 to 10-5
FP example: LD with causal SNP
```{r sim 10-1, out.width = "98%", out.height="95%"}
runtag <- 5
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

True positive example: c1orf109
```{r sim c1, out.width = "98%", out.height="95%"}
runtag <- 4
chrom <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```

# region plot with coloc results
```{r sim 3, out.width = "98%", out.height="95%"}
runtag <- "ukb-s80.45-adi"
i <- 4
chrom <- 5
comparedir <- "/project2/mstephens/causalTWAS/simulations/simulation_ctwas_rss_20210416_compare/"
colocfs <- paste0(comparedir, runtag, "_simu", simutags,".Adipose_Subcutaneous.coloc.result")
plot_all(susiefs[i], pfs[i], phenofs[i], chrom, colocf = colocfs[i], thin = 0.01)
```
## Zoom view
For new simulation settings in 20230322
False positives
```{r sim 4, out.width = "98%", out.height="95%"}
outputdir <- "~/causalTWAS/simulations/simulation_ctwas_rss_20230322/"
runtag <- "ukb-s80.45-adi"
simutags <- paste(2, 1:5, sep = "-")
configtag <- 1

susiefs <- paste0(outputdir, runtag, "_simu", simutags, "_config", configtag, ".susieIrss.txt")
pfs <- paste0(outputdir, runtag, "_simu",simutags)
gwasfs <- paste0(pfs, ".exprgwas.txt.gz")
phenofs <- paste0(outputdir, runtag, "_simu", simutags, "-pheno.Rd")
chrom <- 3
runtag <- 1
plot_all(susiefs[runtag], pfs[runtag], phenofs[runtag], chrom, thin = 0.01)
```
